|

### 2021-05-09 appendix/appendix.Rmd
fixes flow charts

  \node (4th) [exc, right of = inc_1, xshift = 3cm] {Articles excluded during analysis due to nonconforming variables \\ \textbf{(n = 18)}};

\node (inc_2) [phase, below of = inc_1] {Included articles \\ \textbf{(n = 29)}};
  \draw [arrow] (id) -- (1st);
  \draw [arrow] (id) -- (screen);
  \draw [arrow] (screen) -- (2nd);
  \draw [arrow] (screen) -- (elig);
  \draw [arrow] (elig) -- (3rd);
  \draw [arrow] (elig) -- (inc_1);
  \draw [arrow] (inc_1) -- (4th);
  \draw [arrow] (inc_1) -- (inc_2);

@@

```{tikz tikz-ex2, echo=FALSE, cache=TRUE, eval=TRUE, engine.opts = list(template = "tikz2pdf.tex"), fig.width=5, fig.height=2, fig.cap="PRISMA Flow Chart for First Search Strategy: Search String with Terms"}
\usetikzlibrary{shapes.arrows,arrows.meta,positioning,shapes.geometric}
  \begin{tikzpicture} [node distance = 2.7cm, xshift = 1.5]
  \footnotesize
  \linespread{1.0}
  \node (ID) [stage, rotate = 90, yshift = 2cm, xshift = 2.5cm] {\normalsize{Screening 1}};
  \node (SC) [stage, below of = ID, rotate = 90] {\normalsize{Screening 2}};
  \node (EL) [stage, below of = SC, rotate = 90] {\normalsize{Eligibility}};
  \node (INC) [stage2, below of = EL, rotate = 90, xshift = -1.2cm] {\normalsize{Included}};
  \node (id) [phase, right of = ID, xshift = 1cm] {Clean records identified through webscraping  \\ \textbf{(n = 3041)}};
  \node (1st) [exc, right of = id, xshift = 3cm] {Records excluded after reading title, or in languages other than English, book chapters, doctoral theses, and duplicates \\ \textbf{(n = 2603)}};
  \node (screen) [phase, below of = id] {Abstracts assessed for Eligibility \\ \textbf{(n = 483)}};
  \node (2nd) [exc, right of = screen, xshift = 3cm] {Records excluded after reading abstract \\ \textbf{(n = 339)}};
  \node (elig) [phase, below of = screen] {Full-text articles assessed for Eligibility \\ \textbf{(n = 99)}};
  \node (3rd) [exc, right of = elig, xshift = 3cm] {Non-quantitative studies or records using unrelated variables excluded \\ \textbf{(n = 86)}};
  \node (inc_1) [phase, below of = elig] {Preliminary included articles \\ \textbf{(n = 13)}};
  \node (4th) [exc, right of = inc_1, xshift = 3cm] {Articles excluded during analysis due to nonconforming variables \\ \textbf{(n = 10)}};
\node (inc_2) [phase, below of = inc_1] {Included articles \\ \textbf{(n = 3)}};
  \draw [arrow] (id) -- (1st);
  \draw [arrow] (id) -- (screen);
  \draw [arrow] (screen) -- (2nd);
  \draw [arrow] (screen) -- (elig);
  \draw [arrow] (elig) -- (3rd);
  \draw [arrow] (elig) -- (inc_1);
  \draw [arrow] (inc_1) -- (4th);
  \draw [arrow] (inc_1) -- (inc_2);
 \end{tikzpicture}
```

>>>>

  \node (4th) [exc, right of = inc_1, xshift = 3cm] {Articles excluded during analysis due to nonconforming variables \\ \textbf{(n = 19)}};

\node (inc_2) [phase, below of = inc_1] {Included articles \\ \textbf{(n = 28)}};
  \draw [arrow] (id) -- (1st);
  \draw [arrow] (id) -- (screen);
  \draw [arrow] (screen) -- (2nd);
  \draw [arrow] (screen) -- (elig);
  \draw [arrow] (elig) -- (3rd);
  \draw [arrow] (elig) -- (inc_1);
  \draw [arrow] (inc_1) -- (4th);
  \draw [arrow] (inc_1) -- (inc_2);

@@

```{tikz tikz-ex2, echo=FALSE, cache=TRUE, eval=TRUE, engine.opts = list(template = "tikz2pdf.tex"), fig.width=5, fig.height=2, fig.cap="PRISMA Flow Chart for First Search Strategy: Search String with Terms"}
\usetikzlibrary{shapes.arrows,arrows.meta,positioning,shapes.geometric}
  \begin{tikzpicture} [node distance = 2.7cm, xshift = 1.5]
  \footnotesize
  \linespread{1.0}
  \node (ID) [stage, rotate = 90, yshift = 2cm, xshift = 2.5cm] {\normalsize{Screening 1}};
  \node (SC) [stage, below of = ID, rotate = 90] {\normalsize{Screening 2}};
  \node (EL) [stage, below of = SC, rotate = 90] {\normalsize{Eligibility}};
  \node (INC) [stage2, below of = EL, rotate = 90, xshift = -1.2cm] {\normalsize{Included}};
  \node (id) [phase, right of = ID, xshift = 1cm] {Clean records identified through webscraping  \\ \textbf{(n = 3041)}};
  \node (1st) [exc, right of = id, xshift = 3cm] {Records excluded after reading title, or in languages other than English, book chapters, doctoral theses, and duplicates \\ \textbf{(n = 2603)}};
  \node (screen) [phase, below of = id] {Abstracts assessed for Eligibility \\ \textbf{(n = 483)}};
  \node (2nd) [exc, right of = screen, xshift = 3cm] {Records excluded after reading abstract \\ \textbf{(n = 339)}};
  \node (elig) [phase, below of = screen] {Full-text articles assessed for Eligibility \\ \textbf{(n = 99)}};
  \node (3rd) [exc, right of = elig, xshift = 3cm] {Non-quantitative studies or records using unrelated variables excluded \\ \textbf{(n = 86)}};
  \node (inc_1) [phase, below of = elig] {Preliminary included articles \\ \textbf{(n = 13)}};
  \node (4th) [exc, right of = inc_1, xshift = 3cm] {Articles excluded during analysis due to nonconforming variables \\ \textbf{(n = 11)}};
\node (inc_2) [phase, below of = inc_1] {Included articles \\ \textbf{(n = 2)}};
  \draw [arrow] (id) -- (1st);
  \draw [arrow] (id) -- (screen);
  \draw [arrow] (screen) -- (2nd);
  \draw [arrow] (screen) -- (elig);
  \draw [arrow] (elig) -- (3rd);
  \draw [arrow] (elig) -- (inc_1);
  \draw [arrow] (inc_1) -- (4th);
  \draw [arrow] (inc_1) -- (inc_2);
 \end{tikzpicture}
```
